Empirical Evaluation of eval in R

### 2020-08-24 inst/analysis/counts.Rmd
Add own, dependent and core eval calls from CRAN and Kaggle

```{r core-dependent-own-eval}

```

>>>>

```{r core-dependent-own-eval}
all_data <-
    bind_rows(core_data, packages_data, kaggle_data)
    ##filter(is.na(eval_call_srcref))

all_data$package <- map_chr(path_split(all_data$file), function(l) l[[length(l) - 2]])

all_data <-
    all_data %>%
    mutate(core_own_dependent = if_else(eval_source == "core", "core",
                                if_else(eval_source == "base", "core",
                                if_else(package == caller_package, "own",
                                        "dependent"))),
          eval_source)

core_own_dependent <-
    all_data %>%
        group_by(file, core_own_dependent) %>%
        summarize(corpus = first(corpus), eval_calls = sum(nb_ev_calls)) %>%
        ungroup() %>%
        group_by(corpus, core_own_dependent) %>%
        summarize(total_eval_calls = sum(eval_calls),
                  max_eval_calls = max(eval_calls),
                  min_eval_calls = min(eval_calls),
                  avg_eval_calls = mean(eval_calls))

core_own_dependent %>%
pmap_dfr(function(corpus, core_own_dependent, total_eval_calls, max_eval_calls, min_eval_calls, avg_eval_calls) {
    r(str_c(corpus, " ", core_own_dependent, " total eval calls"), total_eval_calls)
    r(str_c(corpus, " ", core_own_dependent, " max eval calls"), max_eval_calls)
    r(str_c(corpus, " ", core_own_dependent, " min eval calls"), min_eval_calls)
    r(str_c(corpus, " ", core_own_dependent, " avg eval calls"), avg_eval_calls)
})

datatable(core_own_dependent)
```
